Regression Discontinuity Design to Measure Incumbency Advantage in US Congressional Elections

### 2023-04-25 paper.qmd
done with 3.1

>>>>

```{r}
#| fig-cap: Three pretreatment covariates versus $t-1$ Democratic vote margin.

test_demos(DF)
```

With no empirical discontinuities in any of the densities under investigation discovered, we can safely assume that the continuity assumption holds in our idealized election model here and feel comfortable applying RDD to estimating effects of incumbency.
